RJObject Paper

### 2014-06-21 Documents/Paper/ms.tex
What happens to parameters when N changes
Slight wording chaneg
The extent of the heavy tailed distribution

\begin{eqnarray}
p(N, \alpha, \{x_i\}) &=& p(N) p(\alpha | N) p(\{x_i\} | \alpha, N) \\
&=& p(N) p(\alpha) \prod_{i=1}^N p(\{x_i\} | \alpha).
\end{eqnarray}

@@

We will assume that the prior for $N$ is a discrete uniform distribution
between 0 and some $N_{\rm max}$, inclusive. The proposal starts by choosing
a new value $N'$ according to
\begin{eqnarray}
N' &=& \textnormal{mod}\left(N + \delta_N, N_{\rm max} + 1\right)
\end{eqnarray}
where $\delta_N$ is drawn from a heavy tailed
distribution.

>>>>

\begin{eqnarray}
p(N, \alpha, \{x_i\}) &=& p(N) p(\alpha | N) p(\{x_i\} | \alpha, N) \\
&=& p(N) p(\alpha) \prod_{i=1}^N p(x_i | \alpha).
\end{eqnarray}

@@

We will assume that the prior for $N$ is a discrete uniform distribution
between 0 and some $N_{\rm max}$, inclusive. The proposal starts by choosing
a new value $N'$ according to
\begin{eqnarray}
N' &=& \textnormal{mod}\left(N + \delta_N, N_{\rm max} + 1\right)
\end{eqnarray}
where $\delta_N$ is drawn from a heavy tailed
distribution. The most probable values of $\delta_N$ are $\pm 1$, but values
of order $N_{\rm max}$ also have some probability, to allow fast exploration
when the target distribution is similar to the prior.

If $N' > N$, the extra parameters needed, $\{x_i\}_{i=N+1}^{N'}$,
are drawn from their prior conditional on the current value of the
hyperparameters, i.e. the interim prior $p(x | \alpha)$.

If $N' < N$, then $N - N'$ objects must be removed from the model. All
of the objects have the same probability of being selected for removal.
